\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx} 
\graphicspath{ {./Images/} } %tells the program what folder to find the images in

\title{Proportional Approval Voting\\DRAFT}
\author{
  Lim Devon\\
  \texttt{h2010076@nushigh.edu.sg}
  \and
  Lee Hong Hao Casper\\
  \texttt{h2010069@nushigh.edu.sg}
  \and
  Kang Jun Jie Joseph\\
  \texttt{h2010059@nushigh.edu.sg}
}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
Introduction, Abstract, Preamble, All will go here.

\section{Questions}

Let there be an election $\boldsymbol{E} = (\boldsymbol{C}, \boldsymbol{V}, \boldsymbol{A})$.
$\boldsymbol{C}$ is the set of all candidates.
$\boldsymbol{V}$ is the set of all voters.
$\boldsymbol{A}$ is the set of all of the voters' Approval Value Functions.\\

$App^{\boldsymbol{E}}_{v}(c)$ is an Approval Value Function for voter $v \in \boldsymbol{V}$ in election $\boldsymbol{E}$.
\begin{equation}
App^{\boldsymbol{E}}_{v} : \boldsymbol{C} \mapsto [-1,1]
\end{equation}
Where a negative value means the voter believes the candidate will have a bad impact, a positive value means the voter believes the candidate will have a positive impact, and 0 means the voter is apathetic towards the candidate. -1 is the worst possible impact and +1 is the best possible impact a candidate may have. It is not neccessary that the least liked and most liked candidates are placed at -1 and +1 respectively, they may just be assigned an arbitrary value between -1 and 1.\\

$Res^{\boldsymbol{E}}_{S}(c)$ is a function, that given election $\boldsymbol{E}$ and voting strategy $S$, provides the result of the vote for candidate $c \in \boldsymbol{C}$.
\begin{gather}
Res^{\boldsymbol{E}}_{S} : \boldsymbol{C} \mapsto [0,1]\\
\sum^{}_{c \in \boldsymbol{C}}{Res^{\boldsymbol{E}}_{S}(c)} = 1
\end{gather}

${IRV}^{\boldsymbol{E}}_{S}(v)$ is a function, that given election $\boldsymbol{E}$ and voting strategy $S$, provides a numerical utility or satisfaction value with the results for voter $v \in \boldsymbol{V}$. We call the output of this function the Individual Reward Value.
\begin{equation}
{IRV}^{\boldsymbol{E}}_{S}(v) = \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}
\end{equation}
It is trivial to show that ${IRV}^{\boldsymbol{E}}_{S} : \boldsymbol{V} \mapsto [-1,1]$. The proof exists but I'm gonna add it later.


\subsection{Question 1}

Let there be a Socially Optimal outcome. It will be defined as the case where
\begin{gather}
App^{\boldsymbol{E}}_{pop}(c) = \sum^{}_{v \in \boldsymbol{V}}{App^{\boldsymbol{E}}_{v}(c)}\\
c_{w} = {argmax}_{c \in \boldsymbol{C}} App^{\boldsymbol{E}}_{pop}(c)\\
Res^{\boldsymbol{E}}_{S}(c_{w}) = 1
\end{gather}\\

Let there be a Social-Positive Optimal outcome. It will be defined as the case where the value of the function below is maximised.
\begin{equation}
\sum^{}_{v \in \boldsymbol{V}}{\left(
\begin{cases}
1, & \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))} > 0\\
0, & {otherwise}
\end{cases}
\right)}
\end{equation}\\

Let us define the Population Reward Value as
\begin{equation}
\sum^{}_{v \in \boldsymbol{V}}{\left(
\sum^{}_{c \in \boldsymbol{C}}{\left(
Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c)
\right)}
\right)}
\end{equation}\\

Are there bounds (either upper or lower) on the difference between the population reward values of the Socially Optimal and Social-Positive Optimal outcomes?

It is known that the Socially Optimal outcome maximises PRV. Wei Shen Me? Yin Wei
\begin{equation}
\begin{aligned}
PRV
&= \sum^{}_{v \in \boldsymbol{V}}{\left(\sum^{}_{c \in \boldsymbol{C}}{\left(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c)\right)}\right)}\\
&= \sum^{}_{c \in \boldsymbol{C}}{\left(\sum^{}_{v \in \boldsymbol{V}}{\left(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c)\right)}\right)}\\
&= \sum^{}_{c \in \boldsymbol{C}}{\left(Res^{\boldsymbol{E}}_{S}(c) \cdot \sum^{}_{v \in \boldsymbol{V}}{\left(App^{\boldsymbol{E}}_{v}(c)\right)}\right)}
\end{aligned}
\end{equation}


\subsection{Strategies and additional outcomes}

\subsubsection{Outcomes}

Let there be a Social-Sign Optimal outcome. It will be defined as the case where the value of the function below is maximised.
\begin{equation}
\sum^{}_{v \in \boldsymbol{V}}{\left(
\begin{cases}
1, & \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))} > 0\\
-1, & \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))} < 0\\
0, & {otherwise}
\end{cases}
\right)}
\end{equation}\\

Let there be a Social-Negative Optimal outcome. It will be defined as the case where the value of the function below is maximised.
\begin{equation}
\sum^{}_{v \in \boldsymbol{V}}{\left(
\begin{cases}
-1, & \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))} < 0\\
0, & {otherwise}
\end{cases}
\right)}
\end{equation}\\

\subsubsection{Strategies}

Strategies differ from outcomes in that strategies lead to outcomes. Therefore, our Optimal Outcomes are theoretical situations that may in fact have no simple strategy that leads to it. It would therefore be of great interest to find the social costs between the outcomes of simple strategies and optimal outcomes.\\

\noindent Here is a list of a few simple strategies we will analyse:
\begin{itemize}
  \item A voter only votes for their highest ranked options. (Strategy 1)
  \item A voter only votes for all candidates except their lowest ranked option. (Strategy 2)
  \item A voter only votes for the options with a positive individual reward weight. (Strategy 3)
\end{itemize}

\subsubsection{More Questions!}

Are there bounds between the social cost of these strategies and outcomes compared to the utilitarian Socially Optimal outcome?\\
Are there bounds between the difference of social costs among these outcomes?

\subsection{Question 2}
We can show that a voter voting for the highest weighted option will never be detrimental to their Individual Reward Value.\\

Consider a voter $v_{1}$. Let $c_{1}$ be their highest weighted candidate, ${argmax}_{c \in \boldsymbol{C}}App^{\boldsymbol{E}}_{v_{i}}(c)$. Now consider 2 cases: (1) $v_{1}$ approves of $c_{1}$, (2) $v_{1}$ does not approve of $c_{1}$. Let $a_{c}$ be the number of approvals candidate $c \in \boldsymbol{C}$ has excluding $v_{1}$'s vote for $c_{1}$. Let $m$ be the total number of votes excluding $v_{1}$'s vote for $c_{1}$.\\

In case (1), 
\begin{equation}
\begin{aligned}
{IRV}^{\boldsymbol{E}}_{(1)}(v_1) 
&= {Res}^{\boldsymbol{E}}_{S}(c_1)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1) + \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_n}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}\\
&= \frac{a_1+1}{m+1}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1) + \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_n}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}
\end{aligned}  
\end{equation}

In case (2), 
\begin{equation}
\begin{aligned}
{IRV}^{\boldsymbol{E}}_{(1)}(v_1) 
&= {Res}^{\boldsymbol{E}}_{S}(c_1)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1) + \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_n}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}\\
&= \frac{a_1}{m}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1) + \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_n}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}
\end{aligned}  
\end{equation}

Therefore,
\begin{equation}\label{IRV_DIFF}
\begin{aligned}
{IRV}^{\boldsymbol{E}}_{(2)}(v_1) - {IRV}^{\boldsymbol{E}}_{(1)}(v_1)
&=  \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}\\
&+ \left(\frac{a_1}{m}-\frac{a_{1}+1}{m+1}\right)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1)\\
\end{aligned}  
\end{equation}

Case (2) will only yield a larger Individual Reward Value than Case (1) if 
\begin{gather}
\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)} + \left(\frac{a_1}{m}-\frac{a_{1}+1}{m+1}\right)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1) > 0\nonumber\\
\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)} > \left(\frac{a_1}{m}-\frac{a_{1}+1}{m+1}\right)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1)
\end{gather}

The maximum value of $\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}$ is attained when ${App}^{\boldsymbol{E}}_{v_1}(c_{n}) = 1 \forall {c} \in \boldsymbol{C} \setminus \{c_1\}$. So,
\begin{equation}
\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)} = \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\right)} = \frac{\sum^{|\boldsymbol{C}|}_{n = 2}{a_{c_{n}}}}{m(m+1)} = \frac{m-a_1}{m(m+1)}
\end{equation}

Therefore,
\begin{equation}
\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)} \leq \beta\cdot\sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\right)} = \beta\cdot\frac{m-a_1}{m(m+1)}
\end{equation}
Where $\beta$ is ${max}_{c \in \boldsymbol{C} \setminus \{c_1\}}\left({App}^{\boldsymbol{E}}_{v_1}(c)\right)$. Note that since we have defined $c_1$ to be the highest weighted candidate for $v_1$, $\beta \leq {App}^{\boldsymbol{E}}_{v_1}(c_1)$.\\

Therefore, substituting this inequality into \eqref{IRV_DIFF},
\begin{equation}
\begin{aligned}
{IRV}^{\boldsymbol{E}}_{(2)}(v_1) - {IRV}^{\boldsymbol{E}}_{(1)}(v_1)
&=  \sum^{|\boldsymbol{C}|}_{n = 2}{\left(\frac{a_{c_{n}}}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_{n})\right)}\\
&+ \left(\frac{a_1}{m}-\frac{a_{1}+1}{m+1}\right)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1)\\
&\leq \beta\cdot\frac{m-a_1}{m(m+1)} + \left(\frac{a_1}{m}-\frac{a_{1}+1}{m+1}\right)\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1)\\
&= \beta\cdot\frac{m-a_1}{m(m+1)} - \frac{m-a_1}{m(m+1)}\cdot{App}^{\boldsymbol{E}}_{v_1}(c_1)\\
&= \left(\beta - {App}^{\boldsymbol{E}}_{v_1}(c_1)\right)\left(\frac{m-a_1}{m(m+1)}\right)
\end{aligned} 
\end{equation}\\

Since $\beta \leq {App}^{\boldsymbol{E}}_{v_1}(c_1)$,
\begin{equation}
     \beta - {App}^{\boldsymbol{E}}_{v_1}(c_1) \leq 0
\end{equation}
and since $m \geq a_1$ and $m \in \mathbb{Z}^+$,
\begin{equation}
     \frac{m-a_1}{m(m+1)} \geq 0
\end{equation}
we show that 
\begin{equation}
     {IRV}^{\boldsymbol{E}}_{(2)}(v_1) - {IRV}^{\boldsymbol{E}}_{(1)}(v_1) \leq \left(\beta - {App}^{\boldsymbol{E}}_{v_1}(c_1)\right)\left(\frac{m-a_1}{m(m+1)}\right) \leq 0
\end{equation}\\

Therefore, we have shown that case (2), where the voter does not vote for their highest weighted candidate, will always result in that voter's Individual Reward Value being lower than or equal to that of case (1), where the voter votes for their highest weighted candidate


\section{Voting Strategies and their Consequences}
\subsection{Grouping the voters}
An important observation is that we can simplify our task of analysing voting strategy performance by grouping voters in accordance with their voting behaviors under the strategy. For example, for the Voting Strategy where voters vote for only the candidate which they've assigned the highest approval weight out of all the candidates, we can group voters into groups according to which candidate they will be voting for. We can then say that there are a certain number of voters in the group, with each voter having an approval weight for a given candidate that is the averaged weight of that candidate among all of the input voters that gave rise to the group.

We can show how such grouping can be used while maintaining the integrity of the PRV value.

Let there be a set of candidates $\boldsymbol{C}$ and voters $\boldsymbol{V}$.

\begin{equation*}
    PRV = \sum^{}_{v \in \boldsymbol{V}}{\left(\sum^{}_{c \in \boldsymbol{C}}{{App}_v(c) \cdot {Res}(c)}\right)}
\end{equation*}

Let us group voters together based on a certain criterion, we will be using their highest ranked candidate for this example.
Let a set of voters that have $c$ as their highet ranked candidate be $V_c$.

\begin{equation*}
\begin{aligned}
PRV &= \sum^{}_{c \in \boldsymbol{C}}{\left(\sum^{}_{v \in V_c}{{IRV}(v)}\right)}\\
&= \sum^{}_{c \in \boldsymbol{C}}{\left({IRV}({v_c}_1)+{IRV}({v_c}_2)+\cdots\right)}\\
&= \sum^{}_{c \in \boldsymbol{C}}{\left(\sum^{}_{c in \boldsymbol{C}}{\left({App}_{{v_c}_1}(c)\cdot Res(c)\right)}+\sum^{}_{c in \boldsymbol{C}}{\left({App}_{{v_c}_2}(c)\cdot Res(c)\right)}+\cdots\right)}\\
&= \sum^{}_{c \in \boldsymbol{C}}{\left(\sum^{}_{c in \boldsymbol{C}}{\left(\sum^{}_{v \in V_c}{{App}_{v}(c)}\right)}+\right)}
\end{aligned}    
\end{equation*}


\subsection{Voting only for the highest weighted candidate}
We will now show how and why we can use such an approach to model elections where only the Highest Approval voting strategy is used, whilst still preserving the PRV value.\\

Let there be an election with $|c|$ candidates. We can construct $|c|$ groups where $|g_c|$ represents a group that supports (will vote for) candidate $c \in \boldsymbol{C}$. We will give each group a population size $|g_c|$ that represents the number of voters that will vote for candidate $c$. The group will be allocated approval weights $\forall c \in \boldsymbol{C}$ that corresponds to the average Approval Weight for each given candidate among the voters associated with that group. Let the set of all such groups be $\boldsymbol{G} = \{g_c | c \in \boldsymbol{C}\}$.

For our theoretical cases, without loss of generality, we can notate the Social Optimal candidate, ${argmax}_{c \in \boldsymbol{C}} \sum^{}_{v \in \boldsymbol{V}}{App^{\boldsymbol{E}}_{v}(c)}$, as $c_1$.

\begin{equation}
     PRV_{SO} = \sum^{}_{g \in \boldsymbol{G}}{\left(App_g(c_1)\cdot|g|\right)} 
\end{equation}

In the strategy where each voter votes only for their top weighted candidate, the result of the election will be proportional to the population size of each group.

\begin{equation}
     PRV_{FirstOnly} = \sum^{}_{g \in \boldsymbol{G}}{\left(\sum^{}_{c \in \boldsymbol{C}}{\left(\frac{|g_c|}{|\boldsymbol{V}|} \cdot App_g(c)\right)} \cdot |g|\right)} 
\end{equation} 

We can create a metric called "Difference" (or "diff" for short) that is the difference between $PRV_{SO}$ and $PRV_{FirstOnly}$.
\begin{equation}\label{DIFF_EQN_0}
\begin{aligned}
{diff} &= PRV_{FirstOnly} - PRV_{SO}\\
&= \sum^{}_{g \in \boldsymbol{G}}{\left(\sum^{}_{c \in \boldsymbol{C}}{\left(\frac{|g_c|}{|\boldsymbol{V}|} \cdot App_g(c)\right)} \cdot |g| - \sum^{}_{g \in \boldsymbol{G}}{\left(App_g(c_1)\cdot|g|\right)}\right)}\\
&= \sum^{}_{g \in \boldsymbol{G}}{\left(\sum^{}_{c \in \boldsymbol{C}}{\left(\frac{|g_c|}{|\boldsymbol{V}|} \cdot App_g(c)\right)} \cdot |g| - App_g(c_1)\cdot|g|\right)}\\
&= \sum^{}_{g \in \boldsymbol{G}}{\left(|g|\left(\sum^{}_{c \in \boldsymbol{C}}{\left(\frac{|g_c|}{|\boldsymbol{V}|} \cdot App_g(c)\right)} - App_g(c_1)\right)\right)}
\end{aligned}
\end{equation}\\

Our goal will be to minimise this $diff$ value.\\

From \eqref{IRV_DIFF}, we can see that having ${App}_{g}(c_1)$ be as large as possible will result in the most negative $diff$ value. While we can have ${App}_{g}(c_1) = 1$, the same cannot necessarily be said for the supporting groups of other candidates. This is because there are additional conditions to maintain the Social Optimal candidate. Therefore, the importance of balancing the ratio of $c_1$ supporters and approval weights of other candidates' supporters is key. 

For one, we can probably say that setting a -1 Approval Weight for all candidates that is neither $c_1$ or that group's highest weighted candidate will result in a more negative PRV as that will make more negative the entire voting population's average approval weight of that non-social optimal candidate, therefore the negative impact of votes towards that non-social optimal candidate will only serve to further drive the PRV value away from the Social Optimal maximum.

We can also make the Approval Weight of $c_1$ for the group that votes for $c_1$ 1 as this will maximise the Social Optimal PRV, therefore maximising the negative effect on the PRV of any detraction of the result share from $c_1$.\\

We will rearrange the diff equation to isolate ${App}_g(c_1)$ and divide $diff$ by $\boldsymbol{V}$ to get a bound on the average discrepancy among the voting populace instead. We will also use $r_c$ to represent the fraction of the voting population that will vote for candidate $c$.
\begin{equation}
    r_c = \frac{|g_c|}{|\boldsymbol{V}|}
\end{equation}
\begin{equation}
\frac{diff}{|\boldsymbol{V}|} = \sum^{}_{c_a \in \boldsymbol{C}}{\left(r_{c_a} \left( \sum^{}_{c_b \in \boldsymbol{C} \setminus \{c_1\}}{\left(r_{c_b} \cdot App_{g_{c_a}}(c_b)\right)} - \left(r_{c_b} + 1\right)App_{g_{c_a}}(c_1) \right) \right)}
\end{equation}

From the equation, we see that making $App_{g_{c_a}}(c_1)$ as positive as possible for all groups will give us the most negative $\frac{diff}{|\boldsymbol{V}|}$. Meanwhile, making $App_{g_{c_a}}(c_b)$ as negative as possible $\forall c_b \in \boldsymbol{C} \setminus \{c_1\}$ for all groups will give us the most negative $\frac{diff}{|\boldsymbol{V}|}$.
However, the condidion that group $g_c$ has candidate $c$ as the candidate with the most positive approval weight has to be maintained. Therefore, let us give all groups that don't have $c_1$ as their highest weighted candidate the following approval weight function.\\

Where $\alpha > \beta$,
\begin{equation}
App_{g_{c_a} \in G \setminus \{g_{c_1}\}} = 
    \begin{cases}
    \alpha, & c_1\\
    \beta, & c_a\\
    -1, & all\ other\ candidates
    \end{cases}
\end{equation}
\begin{equation}
App_{g_{c_1}} = 
    \begin{cases}
    1, & c_1\\
    -1, & all\ other\ candidates
    \end{cases}
\end{equation}

Therefore,
\begin{equation}
\frac{diff}{|\boldsymbol{V}|} = r_{c_1}(2(r_{c_1})) + \sum^{}_{c \in \boldsymbol{C} \setminus \{c_1\}}{\left( r_c \left( (\alpha + 1)r_c + (\beta + 1)(r_{c_1} - 1) \right) \right)}
\end{equation}

\subsection{Minimally Social Positive optimal}

let there be one candidate $c_0$ alongside other candidates $c_x$ who have supporters in set $V_x$ such that:
\\for all $v \in V_x$
\begin{equation}
    App_v(c_x) \geq App_v(c_0) \geq 0
\end{equation}
\\and for all $v \notin V_x$
\begin{equation}
    App_v(c_x) \leq 0
\end{equation}

\subsection{Voting for every candidate except the lowest weighted candidate}

Construct groups according to their lowest weighted candidate. For the purposes of this method, each group's last placed candidate will have a lower $App$ value than all the other candidates. Let there be $|C|$ groups, group $g_c$ will rank candidate $c$ the lowest.

The result for candidate $c$ is $\frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)}$.

Therefore,

\begin{equation}
\begin{aligned}
diff &= \sum^{}_{g \in \boldsymbol{G}}{\left(|g| \cdot \sum^{}_{c \in \boldsymbol{C}}{\left(\frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)} \cdot App_g(c)\right)} - |g| \cdot App_g(c_1) \right)}\\
&= \sum^{}_{g \in \boldsymbol{G}}{\left(|g| \left( \sum^{}_{c \in \boldsymbol{C} \setminus \{c_1\}}{\left(\frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)} \cdot App_g(c)\right)} - \left(1 - \frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)}\right)App_g(c_1) \right) \right)}
\end{aligned}
\end{equation} 

We use $r_c$ to represent the fraction of voters that support candidate $c$.

\begin{gather} 
\frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)} = \frac{1-r_c}{|\boldsymbol{C}|-1} \\
1-\frac{|\boldsymbol{V}|-|g_c|}{|\boldsymbol{V}|(|\boldsymbol{C}|-1)} = \frac{|\boldsymbol{C}|-2+r_{c_1}}{|\boldsymbol{C}|-1}
\end{gather}

Therefore,

\begin{equation}
diff = \sum^{}_{g \in \boldsymbol{G}}{\left(|g| \left( \sum^{}_{c \in \boldsymbol{C} \setminus \{c_1\}}{\left(\frac{1-r_c}{|\boldsymbol{C}|-1} \cdot App_g(c)\right)} - \left(\frac{|\boldsymbol{C}|-2+r_{c_1}}{|\boldsymbol{C}|-1}\right)App_g(c_1) \right) \right)}
\end{equation}

\begin{equation}
\frac{diff}{|\boldsymbol{V}|} = \sum^{}_{g \in \boldsymbol{G}}{\left(r_g \left( \sum^{}_{c \in \boldsymbol{C} \setminus \{c_1\}}{\left(\frac{1-r_c}{|\boldsymbol{C}|-1} \cdot App_g(c)\right)} - \left(\frac{|\boldsymbol{C}|-2+r_{c_1}}{|\boldsymbol{C}|-1}\right)App_g(c_1) \right) \right)}
\end{equation}

If we set every group's approval for $c_1$, excluding $g_{c_1}$, to 1, the detraction of result share from $c_1$ will have the worst impact on PRV. Doing this will not change who is the Social Optimal winner.

Setting the approval weight for every other candidate to be as negative as possible, yet still slightly above the least approved candidate will maximise disconent (maximise IRV reduction) when canidates other than $c_1$ gets to hold a share of the result. This will actually aid in upholding the Social Optimal winner as candidates that are not $c_1$ will have its population approval weight be dragged down.

If we set the group's least approved candidate's approval weight to be -1, this will allow the approval weight for other candidates to be as low as possible (an arbitrarily small quantity more than -1).

Our Approval Weights will be as follows:\\
\begin{itemize}
    \item $App_{g \setminus \{g_{c_1}\}} = $
    \begin{equation}
    \begin{cases}
    1, & c_1\\
    -1, & least\ approved\ candidate\\
    -1 + c, & otherwise
    \end{cases}
    \end{equation}
    \item $App_{g_{c_1}} = $
    \begin{equation}
    \begin{cases}
    -1, & c_1\\
    -1 + c, & least\ approved\ candidate
    \end{cases}
    \end{equation}
\end{itemize}

Where c is an arbitratily small positive value. 

The result of the election will be:

\begin{equation}
{Res}(c) = 
\begin{cases}
    \frac{1-r_{c_1}}{|\boldsymbol{C}|-1}, & c_1\\
    1 - \frac{1-r_{c_1}}{|\boldsymbol{C}|-1}, & all\ other\ candidates\ combined
    \end{cases}
\end{equation}

The average Approval Weight of each candidate among the whole population will be:

\begin{equation}
\begin{aligned}
{App}(c) = 
\begin{cases}
    -\frac{|g_{c_1}}{|\boldsymbol{V}|} + \frac{|\boldsymbol{V}|-|g_{c_1}}{|\boldsymbol{V}|}, & c_1\\
    -1 + c, & all\ other\ candidates
\end{cases}
=
\begin{cases}
    1-2r_{c_1}, & c_1\\
    -1 + c, & all\ other\ candidates
\end{cases}
\end{aligned}
\end{equation}

So, 

\begin{equation}
    \frac{diff}{|\boldsymbol{V}|} = \frac{2(1-r_{c_1})^2}{|\boldsymbol{C}|} - 1 - 1 + 2r_{c_1} = \frac{2(1-r_{c_1})^2}{|\boldsymbol{C}|} + 2r_{c_1} - 2
\end{equation}

\begin{equation}
    \frac{d}{d\, r_{c_1}}\left( \frac{diff}{|\boldsymbol{V}|} \right) = \frac{2(2r_{c_1} + |\boldsymbol{C}| - 3)}{|\boldsymbol{C}| - 1}
\end{equation}

Since $\frac{d^2}{d\, r_{c_1}^2}\left( \frac{diff}{|\boldsymbol{V}|} \right) = \frac{4}{|\boldsymbol{C}| - 1} > 0$, $r_{c_1}$ where $\frac{d}{d\, r_{c_1}}\left( \frac{diff}{|\boldsymbol{V}|} \right) = 0$ will be the local minium. However, when $\frac{d}{d\, r_{c_1}}\left( \frac{diff}{|\boldsymbol{V}|} \right) = 0$, $r_{c_1} = \frac{3-|\boldsymbol{C}|}{2}$. Since $r_{c_1}$ will be negative when $|\boldsymbol{C}| > 3$, our minimum $\frac{diff}{|\boldsymbol{V}|}$ will be when $r_{c_1} = 0$.

Therefore, the lower limit for $\frac{diff}{|\boldsymbol{V}|}$ will be:

\begin{equation}
\begin{cases}
    -\frac{1}{2}, & |\boldsymbol{C}| = 2\\
    \frac{2}{|\boldsymbol{C}|-1} - 2, & |\boldsymbol{C}| \geq 3
\end{cases}
\end{equation}


\subsection{Voting only candidates with a positive individual reward weight}

Let there be an election $\boldsymbol{E}$ with a set of candidates $\boldsymbol{C}$ and a set of voters $\boldsymbol{V}$. 
Let $\boldsymbol{C}$ be split into subsets $\boldsymbol{C}_{1}$, $\boldsymbol{C}_{2}$ and $\boldsymbol{C}_{3}$ (i.e. $\boldsymbol{C}_{1}, \boldsymbol{C}_{2}, \boldsymbol{C}_{3} \subset \boldsymbol{C}$ and $\boldsymbol{C}_{1}+\boldsymbol{C}_{2}+\boldsymbol{C}_{3} \equiv \boldsymbol{C}$) and let $\boldsymbol{V}$ be split into subsets $\boldsymbol{V}_{1}$, $\boldsymbol{V}_{2}$, and $\boldsymbol{V}_{3}$ (i.e. $\boldsymbol{V}_{1}, \boldsymbol{V}_{2}, \boldsymbol{V}_{3} \subset \boldsymbol{V}$ and $\boldsymbol{V}_{1}+\boldsymbol{V}_{2}+\boldsymbol{V}_{3} \equiv \boldsymbol{V}$) with sizes ${m}_{1}$, ${m}_{2}$ and ${m}_{3}$ respectively.
Let the subsets fulfil the following conditions:\\

\begin{itemize}
    \item For all $v \in \boldsymbol{V}_{1}$:\\
    \begin{gather}
    \begin{split}
        \sum^{}_{c \in \boldsymbol{C}_{1}}{App^{\boldsymbol{E}}_{v}(c)} \leq -\frac{{m}_{2}}{{m}_{1}}\sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)}
    \end{split}\\
    App^{\boldsymbol{E}}_{v}(c) \geq 0, c \in \boldsymbol{C}_{1}\\
    App^{\boldsymbol{E}}_{v}(c) \leq 0, c \in \boldsymbol{C}_{2} \cup \boldsymbol{C}_{3}
    \end{gather}
    \item For all $v \in \boldsymbol{V}_{2}$:\\
    \begin{gather}
    \begin{split}
        \sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)} \leq -\frac{{m}_{1}}{{m}_{2}}\sum^{}_{c \in \boldsymbol{C}_{1}}{App^{\boldsymbol{E}}_{v}(c)}
    \end{split}\\
    App^{\boldsymbol{E}}_{v}(c) \geq 0, c \in \boldsymbol{C}_{2}\\
    App^{\boldsymbol{E}}_{v}(c) \leq 0, c \in \boldsymbol{C}_{1} \cup \boldsymbol{C}_{3}
    \end{gather}
    \item For all $v \in \boldsymbol{V}_{3}$:\\
    \begin{gather}
        App^{\boldsymbol{E}}_{v}(c) \leq 0, c \in \boldsymbol{C}
    \end{gather}
\end{itemize}

Given these conditions and voting only candidates with a positive individual reward weight,
\begin{equation}
\begin{aligned}
{IRV}^{\boldsymbol{E}}_{S}(v) &= \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}\\
&= \sum^{}_{c \in \boldsymbol{C}_{1}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}+\sum^{}_{c \in \boldsymbol{C}_{2}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}+\sum^{}_{c \in \boldsymbol{C}_{3}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}
\end{aligned}
\end{equation}\\

As $App^{\boldsymbol{E}}_{v}(c) \leq 0$ for all $c \in \boldsymbol{C}_{3}$, $\sum^{}_{c \in \boldsymbol{C}_{3}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}=0$. 
Additionally, as $App^{\boldsymbol{E}}_{v}(c) \leq 0$ for all $c$ when $v \in \boldsymbol{V}_{3}$, ${IRV}^{\boldsymbol{E}}_{S}(v) \leq 0$ for all $v \in \boldsymbol{V}_{3}$. 
The total number of votes $x$ will be equal to ${m}_{1}{c}_{1}+{m}_{2}{c}_{2}$, where ${c}_{1}$ and ${c}_{2}$ are the sizes of $\boldsymbol{C}_{1}$ and $\boldsymbol{C}_{2}$ respectively. This is because given strategy 3 all $v \in \boldsymbol{V}_{1}$ or $\boldsymbol{V}_{2}$ will vote for all $c \in \boldsymbol{C}_{1}$ or $\boldsymbol{C}_{2}$ respectively i.e. ${c}_{1}$ candidates receive ${m}_{1}$ votes each and ${c}_{2}$ candidates receive ${m}_{2}$ votes each.\\
For $v \in \boldsymbol{V}_{1}$:
\begin{equation}
\begin{split}
    {IRV}^{\boldsymbol{E}}_{S}(v) = \sum^{}_{c \in \boldsymbol{C}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}\\
    = \sum^{}_{c \in \boldsymbol{C}_{1}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}+\sum^{}_{c \in \boldsymbol{C}_{2}}{(Res^{\boldsymbol{E}}_{S}(c) \cdot App^{\boldsymbol{E}}_{v}(c))}\\
    = \sum^{}_{c \in \boldsymbol{C}_{1}}{(\frac{{m}_{1}}{x} \cdot App^{\boldsymbol{E}}_{v}(c))}+\sum^{}_{c \in \boldsymbol{C}_{2}}{(\frac{{m}_{2}}{x} \cdot App^{\boldsymbol{E}}_{v}(c))}\\
    = \frac{{m}_{1}}{x} \cdot \sum^{}_{c \in \boldsymbol{C}_{1}}{App^{\boldsymbol{E}}_{v}(c)}+\frac{{m}_{2}}{x} \cdot \sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)}\\
    \leq \frac{{m}_{1}}{x} \cdot (-\frac{{m}_{2}}{{m}_{1}}\sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)})+\frac{{m}_{2}}{x} \cdot \sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)}\\
    = -\frac{{m}_{2}}{x} \cdot \sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)}+\frac{{m}_{2}}{x} \cdot \sum^{}_{c \in \boldsymbol{C}_{2}}{App^{\boldsymbol{E}}_{v}(c)}\\
    = 0
\end{split}     
\end{equation}\\

A similar proof exists for $v \in \boldsymbol{V}_{1}$.\\
Hence ${IRV}^{\boldsymbol{E}}_{S}(v) \leq 0$ for all $v$, showing that choosing strategy 3 with these conditions will lead to the least Social-Positive, Social-Sign and Social-Sign optimal solutions. 










\end{document}